\chapter{Mixed music and hyper-instruments}\label{mixed-music-and-hyper-instruments}

\section{Framework and historical context}\label{framework-and-historical-context}

Mixed music combines acoustic instruments and electronic elements.

Two different musical contexts:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item sound and formal augmentation (live composing).
\item acoustic instruments augmentation (hyper-instruments).
\end{enumerate}

For both of them we can do it in two ways:

\begin{itemize}
\tightlist
\item superimposing pre-composed electronic sounds and acoustic instruments.
\item acoustic instruments real-time sound processing.
\end{itemize}

For both we have usually:

\begin{itemize}
\tightlist
\item one electronic performer.
\item one sound director.
\item one or more instrumental performers.
\end{itemize}

\section{Sound and formal augmentation}\label{sound-and-formal-augmentation}

In this context we can:


\section{Software model}\label{software-model}
\subsection{Bus and Groups}\label{bus-and-groups}

\section{Feature extraction as control signals}\label{feature-extraction-as-control-signals}
\subsection{Envelope follower}\label{envelope-follower}
\subsection{Pitch follower}\label{pitch-follower}
\subsection{Centroid}\label{centroid}

\section{Classic live electronics sound processing}\label{classic-live-electronics-sound-processing}
\subsection{Ring modulation}\label{ring-modulation}
\subsection{Live recording and playback}\label{live-recording-and-playback}
\subsection{Granular synthesis}\label{granular-synthesis}
\subsection{Delay lines}\label{delay-lines}

\section{Composition sketches proposal}\label{composition-sketches-proposal}
